---
title: "Descriptive statistics of iconicity ratings"
author: "Bodo Winter"
date: "03/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This script is focused _just_ on the norms, without considering any other variables. The `substantive_analysis.Rmd` script is focused on correlating the new norms with other variables to demonstrate construct validity.

## Data and package loading

Load packages:

```{r, warning = FALSE, message = FALSE}
library(tidyverse, quietly = TRUE)
library(patchwork, quietly = TRUE)
library(qqplotr, quietly = TRUE)
```

For reproducibility:

```{r}
packageVersion('tidyverse')
packageVersion('patchwork')
packageVersion('qqplotr')
R.Version()$version.string
```

Load iconicity ratings:

```{r, warning = FALSE, message = FALSE}
# By-word averages:

icon <- read_csv('../ratings/iconicity_ratings_cleaned.csv')
```

For comparison, get the imputed data from Dingemanse & Thompson (2020):

```{r}
ding <- read.csv('../additional_data/dingemanse_thompson_2020.csv',
                stringsAsFactors = FALSE) %>% as_tibble() %>% 
  select(word, ico_imputed, ico_imputed_monomorph)
```

Get the Winter et al. (2017) ratings:

```{r}
winter_2017 <- read.csv('../additional_data/winter_2017_iconicity.csv',
                        stringsAsFactors = FALSE) %>% 
  as_tibble() %>% 
  group_by(Word) %>% 
  summarize(old_iconicity = mean(Iconicity)) %>% 
  rename(word = Word)
```

Get the Perry et al. (2015) ratings:

```{r}
perry_2015 <- read_csv('../additional_data/perry_et_al_2015.csv')
```

## Check the distribution for reporting

How many words?

```{r}
nrow(icon)
```

How many n do we have on average per word?

```{r}
mean(icon$n)
range(icon$n)
```

Check the exact distribution of this:

```{r}
icon %>% 
  count(n)
```

For how much of the dataset do we have at least 10? And then, at least 9?

```{r}
icon %>% 
  count(n) %>% 
  mutate(prop = nn / sum(nn),
         cum_prop = 1 - cumsum(prop))
```

79% of the data have at least >= 10.
98% of the data have at least >= 9.

For reporting, 10 most iconic words:

```{r}
arrange(icon, desc(rating))
```

And 10 least iconic words:

```{r}
arrange(icon, rating)
```

First, grand mean and SD:

```{r}
icon %>% summarize(M = mean(rating),
                   SD = sd(rating),
                   SD = round(SD, 2))
```

First, the iconicity distribution plot, with superimposed normal distribution of exactly the sample mean and standard deviation:

```{r, fig.width = 8, fig.height = 6}
# Main plot with mappings:

icon_p <- icon %>%
  ggplot(aes(x = rating))

# Add density geom and normal curve:

icon_p <- icon_p + 
  geom_density(fill = 'steelblue', alpha = 0.7, col = 'black') +
  stat_function(fun = dnorm,
                args = list(mean = mean(icon$rating),
                            sd = sd(icon$rating)),
                col = 'black',
                linetype = 'dashed',
                size = 1.5)

# Add cosmetics:

icon_p <- icon_p + 
  scale_y_continuous(expand = c(0, 0),
                     breaks = seq(0, 0.5, 0.1),
                     limits = c(0, 0.5)) +
  scale_x_continuous(breaks = 1:7) +
  xlab('Iconicity rating') +
  ylab('Density') +
  theme_classic() +
  
  # Axis labels:
  theme(axis.title.x = element_text(face = 'bold',
                                    size = 16,
                                    margin = margin(t = 10, b = 0,
                                                    l = 0, r = 0)),
        axis.title.y = element_text(face = 'bold',
                                    size = 16,
                                    margin = margin(r = 15, l = 0,
                                                    t = 0, b = 0))) +
  
  # Axis tick marks:
  theme(axis.text.x = element_text(face = 'bold',
                                   size = 12),
        axis.text.y = element_text(face = 'bold',
                                   size = 12))

# Show in markdown:

icon_p

# Save:

ggsave(plot = icon_p,
       filename = '../figures/iconicity_ratings_density.pdf',
       width = 8, height = 6)
```

Make a plot out of this:

```{r, fig.width = 8, fig.height = 6}
# Main plot:

qq_p <- icon %>%
  ggplot(mapping = aes(sample = rating)) +
  stat_qq_band() +
  stat_qq_line() +
  stat_qq_point(alpha = 0.5, size = 0.2)

# Add cosmetics:

qq_p <- qq_p + 
  xlab('Theoretical quantiles') +
  ylab('Sample quantiles') +
  theme_minimal() +
  
  # Axis labels:
  theme(axis.title.x = element_text(face = 'bold',
                                    size = 16,
                                    margin = margin(t = 10, b = 0,
                                                    l = 0, r = 0)),
        axis.title.y = element_text(face = 'bold',
                                    size = 16,
                                    margin = margin(r = 15, l = 0,
                                                    t = 0, b = 0))) +
  
  # Axis tick marks:
  theme(axis.text.x = element_text(face = 'bold',
                                   size = 12),
        axis.text.y = element_text(face = 'bold',
                                   size = 12))

# Show in markdown:

qq_p

# Save:

ggsave(plot = qq_p,
       filename = '../figures/QQ_plot.pdf',
       width = 8, height = 6)
```

Create the Pollock (2018) style plot:

```{r, fig.width = 8, fig.height = 6}
# Main plot:

pollock_p <- icon %>%
  ggplot(aes(x = rating, y = rating_sd)) +
  geom_point(alpha = 0.2)

# Add cosmetics:

pollock_p <- pollock_p + 
  xlab('Mean') +
  ylab('Standard deviation') +
  scale_x_continuous(breaks = 1:7) +
  theme_classic() +
  
  # Axis labels:
  theme(axis.title.x = element_text(face = 'bold',
                                    size = 16,
                                    margin = margin(t = 10, b = 0,
                                                    l = 0, r = 0)),
        axis.title.y = element_text(face = 'bold',
                                    size = 16,
                                    margin = margin(r = 15, l = 0,
                                                    t = 0, b = 0))) +
  
  # Axis tick marks:
  theme(axis.text.x = element_text(face = 'bold',
                                   size = 12),
        axis.text.y = element_text(face = 'bold',
                                   size = 12))

# Show in markdown:

pollock_p

# Save:

ggsave(plot = pollock_p,
       filename = '../figures/pollock_2018.pdf',
       width = 8, height = 6)
```

Create a double plot of normal distribution with Pollock (2018) graph:

```{r, fig.width = 12, fig.height = 6}
# Add titles:

icon_p <- icon_p +
  ggtitle('(a) Iconicity rating distribution') +
  theme(title = element_text(face = 'bold',
                             size = 18,
                             margin = margin(t = 0, b = 15,
                                             r = 0, l = 0)))

pollock_p <- pollock_p +
  ggtitle('(b) Standard deviation by mean') +
  theme(title = element_text(face = 'bold',
                             size = 18,
                             margin = margin(t = 0, b = 15,
                                             r = 0, l = 0)))

# Put into plot together:

figure_1 <- icon_p + plot_spacer() + pollock_p +
  plot_layout(widths = c(8, 1, 8))


# Show in script:

figure_1

# Save:

ggsave(plot = figure_1,
       filename = '../figures/figure1.pdf',
       width = 12, height = 5)
ggsave(plot = figure_1,
       filename = '../figures/figure1.png',
       width = 12, height = 5)
```

## Correlate with old ratings and imputed ratings

Merge this with Winter et al. (2017) iconicity ratings:

```{r}
icon <- left_join(icon, winter_2017)
```

Correlate this:

```{r}
with(icon, cor.test(rating, old_iconicity, use = 'complete.obs'))
```

Merge this with the Dingemanse & Thompson (2020) data to correlate with imputed norms:

```{r}
icon <- left_join(icon, ding)
```

Check against imputed ratings from the Dingemanse & Thompson (2020) file:

```{r}
with(icon, cor.test(rating, ico_imputed, use = 'complete.obs'))
with(icon, cor.test(rating, ico_imputed_monomorph, use = 'complete.obs'))
```

Reasonably high correlations given that this is imputed.

Merge this with the Perry et al. (2015) data:

```{r}
icon <- left_join(icon, perry_2015)
```

Check against the different ratings from Perry et al. (2015):

```{r}
with(icon, cor.test(rating, E1_written, use = 'complete.obs'))
with(icon, cor.test(rating, E2_spoken, use = 'complete.obs'))
with(icon, cor.test(rating, E3_guessing, use = 'complete.obs'))
```

This completes this analysis.



